Tropical Andes plant Lookup Table

### 2023-09-05 code/L1/L1_TropicalAndes_plant_lookupTable.Rmd
add TRNS package code add taxize code

# Load required packages
```{r}

```

# Read in species lists
```{r}
TRY_species <- read.csv(file.path(data_path,"TropicalAndes_TRY_plant_species.csv"))
BIEN_species <- read.csv(file.path(data_path,"TropicalAndes_BIEN_plant_trait_species.csv"))
```

```{r}
#convert species list into vectors
BIEN_species <- BIEN_species[,2]
TRY_species <- TRY_species[,2]
#what is in both
species <- intersect(TRY_species, BIEN_species)
# what doesn't match
all.equal(TRY_species, BIEN_species)

```

>>>>

# Load required packages
```{r}
library(taxize)
library(knitr)
library(TNRS)
```

# Read in species lists
```{r}
TRY_species <- read.csv(file.path(data_path,"TropicalAndes_TRY_plant_species.csv"))
BIEN_species <- read.csv(file.path(data_path,"TropicalAndes_BIEN_plant_trait_species.csv"))
GBIF_species <- read.csv(file.path(data_path,"TropicalAndes_GBIF_plant_species.csv"))
```

```{r}
# convert species list to character
TRY_species_chr <- as.character(TRY_species$x)
BIEN_species_chr <- as.character(BIEN_species$x)
GBIF_species_chr <- as.character(GBIF_species$x)
```

# Using TNRS
```{r}
BIEN_results <- TNRS(taxonomic_names = BIEN_species)
TRY_results <- TNRS(taxonomic_names = TRY_species)
GBIF_results <- TNRS(taxonomic_names = GBIF_species)
```

# Using taxsize
```{r}
GBIF_species_resolved <- resolve(GBIF_species)
TRY_species_resolved <- resolve(TRY_species)
BIEN_species_resolved <- resolve(BIEN_species)
```
